\addchap{Acknowledgements}                 % include abstract in the table of contents (without number)
\sectionmark{Acknowledgements}             % correct section headings

% body

With deep regards and profound respect, I take this opportunity to acknowledge my sincere indebtedness and gratitude to my advisor, Prof. Dr.-Ing. Huang Yuan, for his invaluable guidance, continuous support, critical suggestions and encouragement throughout this work.
When I initially met with Prof. Dr.-Ing. Huang Yuan, he told me the meaning of research, "Search and search again, until you find the truth."
What I did not genuinely understand at that time, after these years work, I can overwhelmingly aware of the meaning
of this word. Non-stop searching with aid of fearless and intrepid spirit would lead to the final success.
My advisor, Prof. Dr.-Ing. Huang Yuan, is such a fearless leader, whose sense of developing direction and expertise in the related area are the essential in steering this work toward success.
Without his unique and inspiring vision, this work would not be what it is.

My special thanks go to Prof. Dr.-Ing. Michael Vormwald, Materials Mechanics Group, TU Darmstadt for reviewing the thesis and providing important corrections.
% I would like to thank Prof. Dr.-Ing.  for chairing the examination committee and organizing the whole procedure.
% The present thesis has been accomplished during my work as a research assistant since Jan. 2011 at University of Wuppertal, Germany.

For the pleasant atmosphere and their help, I wish to express my acknowledgement to the members of Chair of Technical Mechanics at University of Wuppertal, specially Mrs. Magdalene Blucha, colleagues Songyun Ma, Markus Schneider, Heiko Krull, Xiao Li, Huan Li, Ravindra Ambati and Zongzhuan Yao. Thanks a lot for friendship and helpful suggestions.

Finally, I would like to thank my parents for their unconditional support and encouragement on me during these years, and my wife, for her love and sacrifices that have enabled me to reach this day. Words fail to express my appreciation.

%First of all, I would like to to express my foremost and most heartfelt acknowledgment to my academic advisor, Prof. Dr.-Ing. Huang Yuan, for his invaluable guidance and persistent encouragement during my study.
%He provided me a good academic topic to study and also a good working environment.
%When I was confused with some questions, he always gave me the appropriate suggestions.
%With the help of Prof. Dr.-Ing Huang Yuan, I overcome the difficulties and finished my thesis.

%I am grateful to Zongzhuan Yao, now at Bergische Universit\"at Wuppertal, for his explanation and for showing me the programming method of python. On a more personal level, for the pleasant atmosphere, enjoyable time and their help, I would like to express my acknowledgement to the members of Chair of Technical Mechanics at Bergische Universit\"at Wuppertal, specially Huan Li, Xiao Li, Ravindra Ambati, Songyun Ma, Miao Yu, Jie Fang, as well as to Jingqian Ding for proof reading this thesis and support.
%Thanks a lot for friendship and helpful suggestions.

%Finally, my thanks go to my family for all their help and encouragement over the months. 